---
title: "Geomaroc R version"
output: html_notebook
---


*install geomaroc and geomarocdata*
```{r}
#install.packages("geomaroc")
##OR
#install.packages("C:/Users/pc/Downloads/geomaroc_0.1.1.tar.gz", repos = NULL, type = "source")
##install geomarocdata
#install.packages('geomarocdata',repos='https://amineandam04.github.io/drat/', type='source')
```

```{r}
library(geomaroc)
library(ggplot2)
library(readxl)
```

**First, we plot the population of Morocco by region**

Step1 : Import data
```{r}
popByRegion=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx","Region")
head(popByRegion)
```


Step 2 : Use geomaroc to get the coordinates of  regions to plot
```{r}
#Get the coordinates of each region
coordRegion=getMultiRegion(id=c(1:12))
#Merge population data and coordinates
popByRegion= sf::st_sf(merge(popByRegion,coordRegion,by.x = "Region",by.y = "libelle_fr"))
```

Step 3 : Generate the plot using ggplot
```{r}

options(repr.plot.width=1,reper.plot.heigth=0.75)
ggplot(data = popByRegion, aes(fill = Population)) + 
  geom_sf() + 
  #scale_fill_viridis_c(option = "plasma") +
  scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
  #scale_fill_viridis_c(option = "C")+
  geom_sf_text(
    data = popByRegion,
    aes(label = Region),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  #scale_fill_continuous(name="Population(millions)", 
            #low = "lightgreen", high = "darkgreen",limits = c(0,8), 
            #breaks=c(1,2,3,4,5,6,7), na.value = "grey50") +
  labs(title = "  Population of Moroccon  by region, 2014",
       caption = "Data source: HCP",
       fill = "Population") + 
  theme_void()
```

**Now we plot the population of provinces within a region**

**Region: Tanger-Tetouan-Al-Hoceima**

```{r}
poptanj=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx",3)
head(poptanj)
#Get the coordinates of Tanger-Tetouan-Al-Hoceima
coordRegion=getProvince("Tanger-Tetouan-Al-Hoceima")
#Merge population data and coordinates
poptanj= sf::st_sf(merge(poptanj,coordRegion,by.x = "Province",by.y = "libelle_fr"))
```

```{r}
library(rcartocolor)
ggplot() + 
  geom_sf(data = poptanj, aes(fill = Population)) +
  scale_fill_carto_c(palette = "Mint") +
  theme_void() +
  geom_sf_text(
    data = poptanj,
    aes(label = Province),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Tanjer-Tetouan-Al-Hoceima, 2014",
       caption = "Data source: HCP",
       fill = "Population")
```

**Region: Rabat-Sale-Kenitra**

```{r}
popRabat=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx",1)
head(popRabat)
#Get the coordinates of Rabat-Sale-Kenitra
coordRegion=getProvince("Rabat-Sale-Kenitra")
#Merge population data and coordinates
popRabat= sf::st_sf(merge(popRabat,coordRegion,by.x = "Province",by.y = "libelle_fr"))
```
```{r}
ggplot() + 
  geom_sf(data = popRabat, aes(fill = Population)) +
  scale_fill_carto_c(palette = "Sunset") +
  theme_void() +
  geom_sf_text(
    data = popRabat,
    aes(label = Province),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Rabat-Sale-Kenitra, 2014",
       caption = "Data source: HCP",
       fill = "Population")
  
```

**Region : Casablanca-Settat**

```{r}
popCasa=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx",5)
head(popCasa)
#Get the coordinates of Casablanca-Settat
coordRegion=getProvince("Casablanca-Settat")
#Merge population data and coordinates
popCasa= sf::st_sf(merge(popCasa,coordRegion,by.x = "Province",by.y = "libelle_fr"))
```

```{r}
ggplot() + 
  geom_sf(data = popCasa, aes(fill = Population)) +
  scale_fill_carto_c(palette = "TealGrn") +
  theme_void() +
  geom_sf_text(
    data = popCasa,
    aes(label = Province),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population Casablanca-Settat, 2014",
       caption = "Data source: HCP",
       fill = "Population")
  
```

**Region: Fes-Meknes**
```{r}
popfes=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx","FesMeknes")
head(popfes)
#Get the coordinates of Fes-Meknes
coordRegion=getProvince("Fes-Meknes")
#Merge population data and coordinates
popfes= sf::st_sf(merge(popfes,coordRegion,by.x = "Province",by.y = "libelle_fr"))
```

```{r}
ggplot() + 
  geom_sf(data = popfes, aes(fill = Population)) +
  scale_fill_carto_c(palette = "Tropic") +
  theme_void() +
  geom_sf_text(
    data = popfes,
    aes(label = Province),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Fes-Meknes, 2014",
       caption = "Data source: HCP",
       fill = "Population")
  
```

**Region : Oriental**
```{r}
poport=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx","Oriental")
head(poport)
#Get the coordinates of Oriental
coordRegion=getProvince("Oriental")
#Merge population data and coordinates
poport= sf::st_sf(merge(poport,coordRegion,by.x = "Province",by.y = "libelle_fr"))
```


```{r}
ggplot() + 
  geom_sf(data = poport, aes(fill = Population)) +
  scale_fill_carto_c(palette = "Fall") +
  theme_void() +
  geom_sf_text(
    data = poport,
    aes(label = Province),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Oriental, 2014",
       caption = "Data source: HCP",
       fill = "Population")
  
```
**Region :Laayoune-Sakia-El-Hamra**

```{r}
poplay=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx","Laayoun")
head(poplay)
#Get the coordinates of Laayoune-Sakia-El-Hamra
coordRegion=getProvince("Laayoune-Sakia-El-Hamra")
#Merge population data and coordinates
poplay= sf::st_sf(merge(poplay,coordRegion,by.x = "Province",by.y = "libelle_fr"))
```

```{r}
ggplot() + 
  geom_sf(data = poplay, aes(fill = Population)) +
  scale_fill_carto_c(palette = "BrwnYl") +
  theme_void() +
  geom_sf_text(
    data = poplay,
    aes(label = Province),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Laayoune-Sakia-El-Hamra, 2014",
       caption = "Data source: HCP",
       fill = "Population")
```

**Now we plot the population of districts within a province**

**Province: Casablanca**
```{r}
popcasab=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx","Casa")
head(popcasab)
#Get the coordinates of Casablanca
coordRegion=getDistrict("Casablanca")
#Merge population data and coordinates
popcasab= sf::st_sf(merge(popcasab,coordRegion,by.x = "District",by.y = "libelle_fr"))
```

```{r}
ggplot() + 
  geom_sf(data = popcasab, aes(fill = Population)) +
  scale_fill_carto_c(palette = "Mint") +
  theme_void() +
  geom_sf_text(
    data = popcasab,
    aes(label = District),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Casablanca's districts, 2014",
       caption = "Data source: HCP",
       fill = "Population")
  
```

**Province: Tanger-Assilah**
```{r}
poptanjs=read_excel("C:/Users/pc/Desktop/MoroccoMap/geo_example.xlsx","Tanger-assilah")
head(poptanjs)
#Get the coordinates of Tanger-Assilah
coordRegion=getDistrict("Tanger-Assilah")
#Merge population data and coordinates
poptanjs= sf::st_sf(merge(poptanjs,coordRegion,by.x = "District",by.y = "libelle_fr"))
```

```{r}
ggplot() + 
  geom_sf(data = poptanjs, aes(fill = Population)) +
  scale_fill_carto_c(palette = "OrYel") +
  theme_void() +
  geom_sf_text(
    data = poptanjs,
    aes(label = District),
    check_overlap = TRUE,
    size = 3,
    color = "black",fontface = "bold")+
  labs(title = "  Population of Tanger Assilah's districts, 2014",
       caption = "Data source: HCP",
       fill = "Population")
  
```















